A re-examination of the role of friction in the original Social Force Model

### 2019-05-24 paper.tex
agregue parrafo de bibliografia mediciones meca + Pedflow enla intro

@@

>>>>

\textcolor{red}{A lot of research has been done using data from the Mecca pilgrimage.
Although in this work we focused on Ref.~\cite{helbing3}. There were several investigations 
using real data to calibrate parameters of the PedFlow model developed by 
Lohner et al. Ref.~\cite{lohner2}. Recently a paper was published that uses 
the Kalman filter ensemble to adjust the parameters of this model Ref.~\cite{Togashi1}. 
For more information on PedFlow and Mecca pilgrimage measurements
see Refs.~\cite{Boltes,Dridi1,Dridi2,Baqui1,lohner1} }\\

@@

\bibitem{Dridi1}
\textcolor{red}{Dridi, M. (2015) Pedestrian Flow Simulation Validation and
Verification Techniques. Current Urban Studies, 3, 119-134.
doi: 10.4236/cus.2015.32011.}

\bibitem{Dridi2}
\textcolor{red}{Dridi, M. (2015) Simulation of High Density Pedestrian Flow:
A Microscopic Model. Open Journal of Modelling and Simulation,
3, 81-95. doi: 10.4236/ojmsi.2015.33009.}

\bibitem{Baqui1}
\textcolor{red}{Baqui, Muhammad, and Rainald Löhner. "Real-time crowd safety
and comfort management from CCTV images." Real-Time Image and Video Processing 2017.
Vol. 10223. International Society for Optics and Photonics, 2017.}

\bibitem{Togashi1}
\textcolor{red}{Togashi, Fumiya, et al. "Using ensemble Kalman filter to
determine parameters for computational crowd dynamics simulations." 
Engineering Computations 35.7 (2018): 2612-2628.}

\bibitem{lohner2}
\textcolor{red}{L\"ohner, Rainald. "On the modeling of pedestrian motion." 
Applied Mathematical Modelling 34.2 (2010): 366-382.}
